
---
title: "Project -- Dataset and research question"
author: "Team name **(update)**"
date: "July 4, 2016 **(update)**"
output:
  html_document:
    highlight: pygments
    theme: united
---

```{r load-packages, message = FALSE, echo = FALSE}
# load packages
library(dplyr)
library(ggplot2)
```

* * *

## Research question(s)

Type your research questions(s) here:

1. Research question 1
2. Research question 2 (if you have a secondary question)
3. ...

## Dataset description

Type a brief description of your dataset here

## Dataset citation

Include a citation for your dataset here

## Dataset structure

Load the data:

```{r load-data}
# enter the necessary code to load the data

```

Show the structure of your dataset

```{r str-data}
# enter the name of your dataset into the function below, and uncomment
# str(dataset_name)
```

## Data analysis plan

Type a brief plan of your data analysis. For now, all you need to include in this section
is which variables from the dataset you plan to use, and what associations between them 
you will investigate to help answer your research question.