
---
title: "Exploring North Carolina births"
author: "Mine Cetinkaya-Rundel **(update)**"
date: "July 4, 2016 **(update)**"
output: 
  html_document: 
    highlight: pygments
    theme: united
---

## Load packages

```{r load-packages, message = FALSE}
library(dplyr)
library(ggplot2)
library(oilabs)
```

* * *

Load data:

```{r load-nc}
data(nc)
```

### Exercise 1:

Written response goes here.

```{r ex1}
# code goes here
```


### Exercise 2:

Written response goes here.

```{r ex2}
# code goes here
```


### Exercise 3:

Written response goes here.

```{r ex3}
# code goes here
```


### Exercise 4:

Written response goes here.

```{r ex4}
# code goes here
```

### Exercise 5:

Written response goes here.

```{r ex5}
# code goes here
```

### Exercise 6:

Written response goes here.

```{r ex6}
# code goes here
```

### Exercise 7:

Written response goes here.

```{r ex7}
# code goes here
```

### Exercise 8:

Written response goes here.

```{r ex8}
# code goes here
```

### Exercise 9:

Written response goes here.

```{r ex9}
# code goes here
```

### Exercise 10:

Written response goes here.

```{r ex10}
# code goes here
```

### Exercise 11:

Written response goes here.

```{r ex11}
# code goes here
```

### Exercise 12:

Written response goes here.

```{r ex12}
# code goes here
```

### Exercise 13:

Written response goes here.

```{r ex13}
# code goes here
```

### Exercise 14:

Written response goes here.

```{r ex14}
# code goes here
```
